---
title: "Visualizing uncertainty about LGBT poverty"
author: "Connor Gilroy"
date: "`r Sys.Date()`"
output: 
  html_document: 
    theme: paper
---

<style type="text/css">
.main-container {
  max-width: 800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

M.V. Lee Badgett, Soon Kyu Choi, and Bianca D.M. Wilson released a [report](https://williamsinstitute.law.ucla.edu/experts/soon-kyu-choi/lgbt-poverty-us/) for the Williams Institute about LGBT poverty in the United States. They used data from the Behavioral Risk Factor Surveillance System (BRFSS), a major state-by-state health-related survey, to derive population estimates about LGBT and cis-straight poverty rates.

```{r message=FALSE, warning=FALSE, echo=FALSE}
source("lgbt_poverty.R")
```

Using the 95% confidence intervals from p.39 of the report, I added error bars to Figure 2 on p.8: 

```{r echo=FALSE, fig.align='center'}
fig2_version1
```

I also tried confidence strips, using Claus Wilke's `ungeviz` package: 

```{r echo=FALSE, fig.align='center'}
fig2_version2
```

My sense is that this better conveys the *feeling* of uncertainty and how that differs between groups, but others just found it confusing. 

More ideas and examples can be found in [Chapter 16](https://serialmentor.com/dataviz/visualizing-uncertainty.html), "Visualizing Uncertainty," of Wilke's book on data visualization.
 
The code and data for this project can be found in [this GitHub repository](https://github.com/ccgilroy/lgbt-poverty).
